The ITKv4 registration framework

### 2016-07-17 background/background.Rmd
ENH:  IBM presentation.

__Maybe he should have used [ANTs](https://github.com/ntustison/CongressionalFaceTemplates)?__

@@

![](./figures/dthompson.png)

<!--
Notes:
* Book: On Growth and Form
* Descriptive not susceptible to hypothesis testing
* "This book of mine has little need of preface, for indeed it is 'all preface' from beginning to end."
-->

@@

<!--
Notes:
* Book: On Growth and Form
* Descriptive not susceptible to hypothesis testing
* "This book of mine has little need of preface, for indeed it is 'all preface' from beginning to end."
-->

## ANTs family tree

![](./figures/lineage.jpg)

@@

## Initial scope

![](./figures/ants_initial_scope.png)

@@

## Diffeomorphisms:  Occam's razor modeling

![](./figures/sillyputty.png)

_differentiable map with differentiable inverse_

## Diffeomoprhisms:  fine-grained and flexible maps

![](./figures/highresdiffeos.jpg)

<!--
... to correct a misconception about diffeomorphisms ...
-->

## Diffeomorphisms: image parameterization in a metric space

![](./figures/shape_appearance.png)

>>>>

__Maybe they should have used [ANTs](https://github.com/ntustison/CongressionalFaceTemplates)?__

@@

![](./figures/dthompson.png)
-->

<!--
Notes:
* Book: On Growth and Form
* Descriptive
* "This book of mine has little need of preface, for indeed it is 'all preface' from beginning to end."
-->

@@

<!--
## ANTs family tree

![](./figures/lineage.jpg)
-->

@@

<!--
## Initial scope

![](./figures/ants_initial_scope.png)
-->

@@

### 2016-07-17 background/people2.Rmd
ENH:  IBM presentation.

# Founding developers

##  Brian and Edie

![](./figures/brian_and_edie_sedgwick.jpg)

<!--
Notes:
* Velvet Underground (Edie Segwick, Andy Warhol, others)
* Brain--visionary,brilliant.
* New college in Florida --- degree in Physics and Literature(?)
* Went to Siemens and got kicked out, fortunately, by ???  "You need to get a doctorate."
* Jim Gee first graduate student
* Jim wanted to work on FEM registration
  - side tangent:  Jim''s notebooks of FEM registration code
-->

## Nick and Bruce

![](./background/figures/brucelee.png)

<!--
NOtes:
* Not much to say
  - did graduate work at the University of Virginia (hyper. gas lungs)
  - Washington University in St. Louis (cardiac)
  - actually bombed interview with Siemens
  - 2004: Jim offered a job without an interview (long term collaboration)
  - wrote graph cuts for ITK in a month
-->

##  Brian and Nick

<BR><BR>

@@

## ANTs long term collaborators

![](./figures/antscollab.jpg)

>>>>

# Developers and collaborators

##  Founders:  Brian and Nick

@@

----

![](./figures/antsCollaborators2.png)

### 2016-07-17 competitions/competitions.Rmd
ENH:  IBM presentation.

# Competitions

@@

@@

* [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496)
* [EMPIRE 2010](http://empire10.isi.uu.nl)
* [Multi-Atlas Label Challenge 2012](https://masi.vuse.vanderbilt.edu/workshop2012/index.php/Main_Page)
* [SATA Challenge 2013](https://masi.vuse.vanderbilt.edu/workshop2013/index.php/MICCAI_2013_SATA_Challenge_and_Workshop:Current_events)
* [BRATS 2013](http://martinos.org/qtim/miccai2013/)
* [STACOM 2014 MoCo Challenge](http://www.cardiacatlas.org/web/stacom2014/moco-introduction)

@@

<!--
* 14 algorithms
* publicly available data
* different labeling protocols
* developers tune their own algorithms
-->

@@

<span style="color:green;">__Results__</span>

@@

Optimal symmetric multimodal templates and concatenated random forests for
supervised brain tumor segmentation (simplified) with ANTsR, _Neuroinformatics_.

>>>>

<!--
# Competitions
-->

<!--

@@

-->

@@

* [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496): MRI brain registration

* [EMPIRE 2010](http://empire10.isi.uu.nl):  CT lung registration

* [Multi-Atlas Label Challenge 2012](https://masi.vuse.vanderbilt.edu/workshop2012/index.php/Main_Page):  MRI brain registration and segmentation

* [SATA Challenge 2013](https://masi.vuse.vanderbilt.edu/workshop2013/index.php/MICCAI_2013_SATA_Challenge_and_Workshop:Current_events): MRI cardiac and canine hind leg registration

* [BRATS 2013](http://martinos.org/qtim/miccai2013/): Multi-modal MRI brain segmentation

* [STACOM 2014 MoCo Challenge](http://www.cardiacatlas.org/web/stacom2014/moco-introduction):  MRI cardiac motion estimation

@@

* 14 algorithms
* publicly available data
* different labeling protocols
* developers tune their own algorithms

@@

@@

[Tustison, et al., Optimal symmetric multimodal templates and concatenated random forests for
supervised brain tumor segmentation (simplified) with _ANTsR_, _Neuroinformatics_.](http://www.ncbi.nlm.nih.gov/pubmed/25433513)

### 2016-07-17 evaluation/antsvfreesurfer2.Rmd
ENH:  IBM presentation.

---
title: ANTs brain morphology
author: Nick (UVa) and Brian (Penn)
bibliography: REFERENCES.bib
logo:    figures/antsLogoBase.png
output:
  beamer_presentation:
    colortheme: dolphin
    fonttheme:  structurebold
    highlight: tango
    incremental: yes
    theme:  AnnArbor
    includes:
      in_header: mystyle.tex
    toc: yes
  pdf_document:
    toc: true
    highlight: zenburn
  html_document:
    toc: true
    theme: readable
  revealjs_presentation:
    pandoc_args: [ "--slide-level", "2" ]
    incremental: true
    widescreen: true
    smaller: false
    theme: night
    transition: fade
    highlight: zenburn
    center: true
    self_contained: false
  ioslides_presentation:
    css: atk.css
    incremental: false
    widescreen: true
    smaller: false
    fig_width: 5
---

```{r global options, include=FALSE}
library(rmarkdown)
library(knitr)
figpath<-'figures/'
opts_chunk$set(fig.width=9, fig.height=6, fig.path=figpath,
               warning=FALSE, message=FALSE)
```

@@

* Sandy, Brian, and <span style="color:red;">DiReCT</span>
    + used other tools such as FMRIB Automated Segmentation Tool (FAST)
    + `KellySlater.cxx`
* pipedream scripts "adequate for Penn data."
* `KellyKapowski.cxx` and `antsCorticalThickness.sh`
* _"Let's evaluate on open data."_
* and, eventually, _"Let's compare with FreeSurfer."_

@@

<!--
Comparison with de facto standard FreeSurfer package.  Note the difference in separation of
the gray matter from the surrounding CSF.  (0 failures out of 1205 scans)
-->

@@

<!--
Randomly selected healthy individuals.  ```Atropos``` gets good performance across ages.
-->

## Cortical thickness estimation

@@

<!--
In contrast to FreeSurfer which warps coupled surface meshes to segment the gray matter, *ANTs* diffeomorphically registers the white matter to the combined gray/white matters while simultaneously estimating thickness.
-->

## _But without ground truth, how does one evaluate the pipeline?_

@@

## Open science prinicples

>>>>

# Putting it all together---the ANTs cortical thickness pipeline

@@

* Sandy, Brian, and <span style="color:red;">DiReCT</span>
    + used other tools such as FMRIB Automated Segmentation Tool (FAST)
    + `KellySlater.cxx`
* pipedream scripts "adequate for Penn data."
* `KellyKapowski.cxx` and `antsCorticalThickness.sh`
* _"Let's evaluate on open data."_
* and, eventually, _"Let's compare with FreeSurfer."_
-->

@@

Comparison with de facto standard FreeSurfer package.  Note the difference in separation of
the gray matter from the surrounding CSF.  (0 failures out of 1205 scans)
-->

<!--

@@

Randomly selected healthy individuals.  ```Atropos``` gets good performance across ages.
-->

## Cortical thickness maps

@@

In contrast to FreeSurfer which warps coupled surface meshes to segment the gray matter,
*ANTs* diffeomorphically registers the white matter to the combined gray/white matters
while simultaneously estimating thickness.

----

_But without ground truth, how does one evaluate the pipeline?_

@@

## Open science principles

### 2016-07-17 evaluation/antsvfreesurfer2_extra.Rmd
ENH:  IBM presentation.

##

*  "_Hey, can I have the FreeSurfer measurements for the entorhinal cortex?_"  Sure, why not?

*  "_I was wondering if you would make available the CT in each ROI for each subject..._" Sure, why not?  Would you also like the surface areas and volumes?

##  What about using both the T1 & T2?

@@

## So how does ATITH compare with ANTs, FS?

## Prediction from cortical thickness data

@@

## And currently brewing on the UVa cluster...

_Does [denoising](http://www.ncbi.nlm.nih.gov/pubmed/20027588) help?_

@@

* ``itkAdaptiveNonLocalMeansDenoisingImageFilter.h``

* ``itkAdaptiveNonLocalMeansDenoisingImageFilter.hxx``

@@

@@

## it is absolutely free!

@@

_(as in speech, not beer)_

## We'll discuss more this afternoon

https://github.com/ntustison/antsCorticalThicknessExample

>>>>

<!--
##  What about using both the T1 & T2?
-->

@@

-->

<!--
----

_So how does ATITH compare with ANTs, FS?_
-->
## Prediction from cortical thickness data

@@

## _Does [denoising](http://www.ncbi.nlm.nih.gov/pubmed/20027588) help?_

@@

@@

## _Does [denoising](http://www.ncbi.nlm.nih.gov/pubmed/20027588) help?_

![](./evaluation/figures/rfRmseDenoise05.png)

-->

## Longitudinal processing

![](./longitudinal/figures/longitudinalPipeline.png)

@@

## it is absolutely ``free''!

@@

----

*  "_Hey, can I have the FreeSurfer measurements for the entorhinal cortex?_"
Sure, why not?---[Hasan, et al., J Neuroimaging](http://www.ncbi.nlm.nih.gov/pubmed/26565394)

### 2016-07-17 ibm.Rmd
ENH:  IBM presentation.

---
title: <span style="color:red;">ANTs:</span><br /> A brief retrospective
author: Nick Tustison
bibliography: REFERENCES.bib
logo:    figures/antsLogoBase.png
output:
  beamer_presentation:
    colortheme: dolphin
    fonttheme:  structurebold
    highlight: tango
    incremental: yes
    theme:  AnnArbor
    includes:
      in_header: mystyle.tex
    toc: yes
  pdf_document:
    toc: true
    highlight: zenburn
  html_document:
    toc: true
    theme: readable
  revealjs_presentation:
    pandoc_args: [ "--slide-level", "2" ]
    incremental: true
    widescreen: true
    smaller: false
    theme: night
    transition: fade
    highlight: zenburn
    center: true
    self_contained: false
  ioslides_presentation:
    css: atk.css
    incremental: false
    widescreen: true
    smaller: false
    fig_width: 5
---
# Founding developers

##  Brian and Nick

<BR><BR>

@@

<!--
NOtes:
* However, it is not just us
* Other people have done quite a bit
* and others who are not shown such as Arman
-->
# ANTs lineage

@@

<!--
Notes:
* Book: On Growth and Form
* Descriptive not susceptible to hypothesis testing
* "This book of mine has little need of preface, for indeed it is 'all preface' from beginning to end."
-->

@@

## ANTs family tree

![](./figures/lineage.jpg)

@@

# Major tools

@@

<BR><BR>
<span style="color:red;">_"Papers are just advertisements for the science."_</red>
<BR>

@@

## Diffeomoprhisms:  fine-grained and flexible maps

@@

## ```antsMultivariateTemplateConstruction2.sh```

```bash
$ antsMultivariateTemplateConstruction2.sh

@@

antsMultivariateTemplateConstruction2.sh -d ImageDimension -o OutputPrefix <other options> <images>

Compulsory arguments (minimal command line requires SGE/PBS cluster, otherwise use -c and
  -j options):

@@

     -o:  OutputPrefix; A prefix that is prepended to all output files.

@@

     -a   image statistic used to summarize images (default 1)
          0 = mean
          1 = mean of normalized intensities
          2 = median

     -b:  Backup images and results from all iterations (default = 0):  Boolean to save
          the transform files, bias corrected, and warped images for each iteration.

     -c:  Control for parallel computation (default 0):
          0 = run serially
          1 = SGE qsub
          2 = use PEXEC (localhost)
          3 = Apple XGrid
          4 = PBS qsub

     -e   use single precision ( default 1 )

     -g:  Gradient step size (default 0.25): smaller in magnitude results in more
          cautious steps.

     -i:  Iteration limit (default 4): iterations of the template construction
          (Iteration limit)*NumImages registrations.

     -j:  Number of cpu cores to use locally for pexec option (default 2; requires "-c 2")

     -k:  Number of modalities used to construct the template (default 1):  For example,
          if one wanted to create a multimodal template consisting of T1,T2,and FA
          components ("-k 3").

     -w:  Modality weights used in the similarity metric (default = 1): specified as
          e.g. 1x0.5x0.75.

     -q:  Max iterations for each pairwise registration (default = 100x100x70x20):
          specified in the form ...xJxKxL where
            J = max iterations at coarsest resolution (here, reduced by power of 2^2)
            K = middle resolution iterations (here, reduced by power of 2)
            L = fine resolution iteratioxns (here, full resolution).
          Finer resolutions take much more time per iteration than coarser resolutions.

     -f:  Shrink factors (default = 6x4x2x1):  Also in the same form as -q max iterations.
          Needs to have the same number of components.

     -s:  Smoothing factors (default = 3x2x1x0):  Also in the same form as -q max
          iterations.  Needs to have the same number of components.

     -n:  N4BiasFieldCorrection of moving image: 0 == off, 1 == on (default 1).

@@

     -r:  Do rigid-body registration of inputs before creating template (default 0):
          0 == off 1 == on. Only useful when you do not have an initial template

     -l:  Use linear image registration stages during the pairwise (template/subject)
          deformable registration.  Otherwise, registration is limited to SyN or
          B-spline SyN (see '-t' option).  This is '1' by default.

     -m:  Type of similarity metric used for registration (default = CC):  Options are
            CC = cross-correlation
            MI = mutual information
            MSQ = mean square difference
            DEMONS = demon's metric
          A similarity metric per modality can be specified.  If the CC metric is chosen,
          one can also specify the radius in brackets, e.g. '-m CC[4]'.

     -t:  Type of transformation model used for registration (default = SyN):  Options are
            SyN = Greedy SyN
            BSplineSyN = Greedy B-spline SyN
            TimeVaryingVelocityField = Time-varying velocity field
            TimeVaryingBSplineVelocityField = Time-varying B-spline velocity field

     -u:  Walltime (default = 20:00:00):  Option for PBS qsub specifying requested time
          per pairwise registration.

     -v:  Memory limit (default = 8gb):  Option for PBS qsub specifying requested memory
          per pairwise registration.

@@

     -z:  Use this this volume as the target of all inputs. When not used, the script
          will create an unbiased starting point by averaging all inputs. Use the full
          path.
          For multiple modalities, specify -z modality1.nii.gz -z modality2.nii.gz ...
          in the same modality order as the input images.

@@

antsMultivariateTemplateConstruction2.sh -d 3 -i 3 -k 1 -f 4x2x1 -s 2x1x0vox -q 30x20x4 -t SyN  -m CC -c 0 -o MY sub*avg.nii.gz

Multimodal example:

antsMultivariateTemplateConstruction2.sh -d 3 -i 3 -k 2 -f 4x2x1 -s 2x1x0vox -q 30x20x4 -t SyN -z t1.nii.gz -z t2.nii.gz  -m CC -c 0 -o MY templateInput.csv

where templateInput.csv contains

subjectA_t1.nii.gz,subjectA_t2.nii.gz
subjectB_t1.nii.gz,subjectB_t2.nii.gz
...

@@

--------------------------------------------------------------------------------------
Script by Nick Tustison
--------------------------------------------------------------------------------------
Apple XGrid support by Craig Stark
--------------------------------------------------------------------------------------
```

@@

@@

## Cortical thickness estimation

@@

*  "_Hey, can I have the FreeSurfer measurements for the entorhinal cortex?_"  Sure, why not?

*  "_I was wondering if you would make available the CT in each ROI for each subject..._" Sure, why not?  Would you also like the surface areas and volumes?

##  What about using both the T1 & T2?

@@

## So how does ATITH compare with ANTs, FS?

@@

@@

# Joint label/intensity fusion

## Multi-atlas labeling

* ``Correct'' images
    * motion correction
    * lesions
* Project atlas set intensity signature
-->

>>>>

---
title: \`\`Dr. Tustison (UVA) presentation\'\'
subtitle:
author: Nick Tustison
bibliography: REFERENCES.bib
output:
  beamer_presentation:
    colortheme: dolphin
    fonttheme:  professionalfonts
    highlight: tango
    incremental: false
    theme:  AnnArbor
    includes:
      in_header: mystyle.tex
 #   toc: yes
    keep_tex: yes
    slide_level: 2
---

# Developers and collaborators

##  Founders:  Brian and Nick

@@

<!--
NOtes:
* However, it is not just us
* Other people have done quite a bit
* and others who are not shown such as Arman
-->

# Why would you care?

## \`\`Free beer\'\'

![](./licenses/figures/freebeerfreespeech.jpg)

-->

## Software for medical image analysis

* [FSL](http://fsl.fmrib.ox.ac.uk/fsldownloads/)

* [SPM](http://www.fil.ion.ucl.ac.uk/spm/software/)

* [FreeSurfer](http://www.fil.ion.ucl.ac.uk/spm/software/)

* [MIPAV](http://mipav.cit.nih.gov)

* [AFNI](https://afni.nimh.nih.gov/afni)

* Slicer, Elastix, SimpleITK, ANTs $\longleftrightarrow$ [Insight Toolkit](http://www.itk.org)

* Many more at [idoimaging.com](http://idoimaging.com)

## [FSL](http://fsl.fmrib.ox.ac.uk/fsldownloads/)

> No part of the Software may be reproduced, modified, transmitted or
> transferred in any form or by any means, electronic or mechanical,
> without the express permission of the University. The permission of
> the University is not required if the said reproduction, modification,
> transmission or transference is done without financial return, ...
> You may be held legally responsible for any copyright infringement
> that is caused or encouraged by your failure to abide by these terms
> and conditions.
>
> __You are not permitted under this Licence to use this Software
> commercially.__

## [SPM](http://www.fil.ion.ucl.ac.uk/spm/software/)

> SPM is free but copyright software, distributed under the terms of
> the GNU General Public Licence as published by the Free Software
> Foundation (either version 2, as given in file spm_LICENCE.man,
> or at your option, any later version). Further details on "copyleft"
> can be found at http://www.gnu.org/copyleft/. In particular, SPM is
> supplied as is. No formal support or maintenance is provided or implied.

> "Copyleft" says that anyone who redistributes the software, with or
> without changes, must pass along the freedom to further copy and change
> it. Copyleft guarantees that every user has freedom... __it is illegal to
> distribute the improved version except as free software__...

## [FreeSurfer](http://www.fil.ion.ucl.ac.uk/spm/software/)

> The license granted in this Software License includes without limitation
> the right to (i) incorporate the Software into proprietary programs
> (subject to any restrictions applicable to such programs), (ii) add
> your own copyright statement to your modifications of the Software, and
> (iii) provide additional or different license terms and conditions in your
> sublicenses of modifications of the Software; provided that in each case your
> use, reproduction or distribution of such modifications otherwise complies
> with the conditions stated in this Software License.

## [ANTs](https://github.com/stnava/ANTs/blob/master/ANTSCopyright.txt)

> Redistribution and use in source and binary forms, with or without
> modification, are permitted provided that the following conditions
> are met:
> 1. _Redistributions of source code must retain the above copyright
>   notice, this list of conditions and the following disclaimer._
> 2. _Redistributions in binary form must reproduce the above copyright
>   notice, this list of conditions and the following disclaimer in the
>   documentation and/or other materials provided with the distribution._
> 3. _Neither the name of the consortium nor the names of its contributors
>  may be used to endorse or promote products derived from this software
>  without specific prior written permission._

## [ITK](https://itk.org/ITK/project/licenseversion1.html)

> The license of the Insight Toolkit is an open-source Apache 2.0 license. It
> allows unrestricted use, including use in commercial products.
> Starting with ITK 4.0, The Insight Toolkit is distributed under the Apache 2.0
> license approved by the Open Source Initiative (OSI).

-->

<!--
# Competitions
-->

## Algorithmic fight club

![](./competitions/figures/fightclub.jpg)

-->

## International competitions

* [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496): MRI brain registration

* [EMPIRE 2010](http://empire10.isi.uu.nl):  CT lung registration

* [Multi-Atlas Label Challenge 2012](https://masi.vuse.vanderbilt.edu/workshop2012/index.php/Main_Page):  MRI brain registration and segmentation

* [SATA Challenge 2013](https://masi.vuse.vanderbilt.edu/workshop2013/index.php/MICCAI_2013_SATA_Challenge_and_Workshop:Current_events): MRI cardiac and canine hind leg registration

* [BRATS 2013](http://martinos.org/qtim/miccai2013/): Multi-modal MRI brain segmentation

* [STACOM 2014 MoCo Challenge](http://www.cardiacatlas.org/web/stacom2014/moco-introduction):  MRI cardiac motion estimation

<!--- ![](./evaluation/figures/evalhistory.png) -->

## Klein, NeuroImage 2009

![](./competitions/figures/nihms-130679-f0001.jpg)

* 14 algorithms
* publicly available data
* different labeling protocols
* developers tune their own algorithms

## Klein results

![](./competitions/figures/KleinResults2009.png)

## Take-away message

_"One of the most significant findings of this study is that the relative performances of
the registration methods under comparison appear to be little affected by the choice of
subject population, labeling protocol, and type of overlap measure....  ART, SyN, IRTK, and
SPM's DARTEL Toolbox gave the best results according to overlap and distance measures,
with ART and SyN delivering the most consistently high accuracy across subjects and label sets."_

## EMPIRE 2010

![](./competitions/figures/EMPIRE10criteria.png)

* Alignment of lung boundaries,

* major fissures,

* annotated landmark pairs, and

* topology of displacement field.

## EMPIRE 2010 results

![](./competitions/figures/EMPIRE10Results.png)

## Multi-atlas 2012

## SATA 2013

Three very different problem domains

![](./competitions/figures/SATA_data.png)

## BRATS 2013

![](./competitions/figures/brats2013results1.png)

## BRATS 2013 results

![](./competitions/figures/brats2013results2.png)

[Tustison, et al., Optimal symmetric multimodal templates and concatenated random forests for
supervised brain tumor segmentation (simplified) with _ANTsR_, _Neuroinformatics_.](http://www.ncbi.nlm.nih.gov/pubmed/25433513)

## STACOM 2014

![](./competitions/figures/image_gallery.jpg)

-->

<!--- A great opportunity to showcase a [new SyN variant](http://www.ncbi.nlm.nih.gov/pubmed/24409140) -->
# ANTs lineage

@@

<!--
Notes:
* Book: On Growth and Form
* Descriptive
* "This book of mine has little need of preface, for indeed it is 'all preface' from beginning to end."
-->

@@

<!--
## ANTs family tree

![](./figures/lineage.jpg)
-->

@@

# Major ANTs utilities

@@

<BR><BR>
_\`\`Papers are just advertisements for the science.\'\'_
<BR>

## Neuro tools

![](./tools/figures/coreANtsToolsNeuro.png)

## Pulmonary tools

![](./tools/figures/coreANtsToolsLung.png)

@@

-->

## Diffeomoprhisms:  differentiable map with diff. inverse

@@

## ```antsMultivariateTemplateConstruction.sh```

```bash
$ antsMultivariateTemplateConstruction.sh

@@

antsMultivariateTemplateConstruction.sh -d ImageDimension -o OUTPREFIX <other options> <images>

Compulsory arguments (minimal command line requires SGE cluster, otherwise use -c & -j options):

@@

     -o:  OUTPREFIX; A prefix that is prepended to all output files.

@@

     -c:  Control for parallel computation (default 1) -- 0 == run serially,  1 == SGE qsub,
          2 == use PEXEC (localhost), 3 == Apple XGrid, 4 == PBS qsub, 5 == SLURM

     -g:  Gradient step size (default 0.25) -- smaller in magnitude results in more cautious steps

     -i:  Iteration limit (default 4) -- iterations of the template construction (Iteration limit)*NumImages registrations.

     -j:  Number of cpu cores to use (default 2; -- requires "-c 2")

     -k:  Number of modalities used to construct the template (default 1)

     -w:  Modality weights used in the similarity metric (default = 1) --- specified as e.g. 1x0.5x0.75

     -m:  Max-iterations in each registration

     -n:  N4BiasFieldCorrection of moving image (default 1) -- 0 == off, 1 == on

@@

     -r:  Do rigid-body registration of inputs before creating template (default 0) -- 0 == off 1 == on. Only useful when
          you do not have an initial template

     -s:  Type of similarity metric used for registration.

     -t:  Type of transformation model used for registration.

@@

     -z:  Use this this volume as the target of all inputs. When not used, the script
          will create an unbiased starting point by averaging all inputs. Use the full path!

     -b:  Boolean for saving iteration output to directories (default = 0).

@@

antsMultivariateTemplateConstruction.sh -d 3 -m 30x50x20 -t GR -s CC -c 1 -o MY -z InitialTemplate.nii.gz  *RF*T1x.nii.gz

- In this example 30x50x20 iterations per registration are used for template creation (that is the default)
- Greedy-SyN and CC are the metrics to guide the mapping.
- Output is prepended with MY and the initial template is InitialTemplate.nii.gz (optional).
- The -c option is set to 1, which will result in using the Sun Grid Engine (SGE) to distribute the computation.
- if you do not have SGE, read the help for multi-core computation on the local machine, or Apple X-grid options.

@@

--------------------------------------------------------------------------------------
script adapted by N.M. van Strien, http://www.mri-tutorial.com | NTNU MR-Center
multivariate template adaption by Nick Tustison
--------------------------------------------------------------------------------------
Apple XGrid support by Craig Stark
--------------------------------------------------------------------------------------
```

@@

## ```DenoiseImage``` --- contribution from Jose Manjon

```bash
$ DenoiseImage --help

     -n, --noise-model Rician/(Gaussian)
          Employ a Rician or Gaussian noise model.

     -x, --mask-image maskImageFilename
          If a mask image is specified, denoising is only performed in the mask region.

     -p, --patch-radius 1
                        1x1x1
          Patch radius. Default = 1x1x1

     -r, --search-radius 3
                         3x3x3
          Search radius. Default = 3x3x3.

     --help
          Print the help menu.
          <VALUES>: 1

```

* ``Correct'' images

    * motion correction

    * ``remove'' lesions

* Project atlas set intensity signature

* Use in ``corrective learning''

## ```antsJointFusion``` --- contribution from Hongzhi Wang (with some added features)

```bash
$ antsJointFusion --help

COMMAND:
     antsJointFusion
          antsJointFusion is an image fusion algorithm developed by Hongzhi Wang and Paul
          Yushkevich which won segmentation challenges at MICCAI 2012 and MICCAI 2013. The
          original label fusion framework was extended to accommodate intensities by Brian
          Avants. This implementation is based on Paul's original ITK-style implementation
          and Brian's ANTsR implementation. References include 1) H. Wang, J. W. Suh, S.
          Das, J. Pluta, C. Craige, P. Yushkevich, Multi-atlas segmentation with joint
          label fusion IEEE Trans. on Pattern Analysis and Machine Intelligence, 35(3),
          611-623, 2013. and 2) H. Wang and P. A. Yushkevich, Multi-atlas segmentation
          with joint label fusion and corrective learning--an open source implementation,
          Front. Neuroinform., 2013.

     -t, --target-image targetImage
                        [targetImageModality0,targetImageModality1,...,targetImageModalityN]
          The target image (or multimodal target images) assumed to be aligned to a common
          image domain.

     -g, --atlas-image atlasImage
                       [atlasImageModality0,atlasImageModality1,...,atlasImageModalityN]
          The atlas image (or multimodal atlas images) assumed to be aligned to a common
          image domain.

     -l, --atlas-segmentation atlasSegmentation
          The atlas segmentation images. For performing label fusion the number of
          specified segmentations should be identical to the number of atlas image sets.

     -a, --alpha 0.1
          Regularization term added to matrix Mx for calculating the inverse. Default =
          0.1

     -b, --beta 2.0
          Exponent for mapping intensity difference to the joint error. Default = 2.0

     -r, --retain-label-posterior-images (0)/1
          Retain label posterior probability images. Requires atlas segmentations to be
          specified. Default = false

     -f, --retain-atlas-voting-images (0)/1
          Retain atlas voting images. Default = false

     -c, --constrain-nonnegative (0)/1
          Constrain solution to non-negative weights.

     -p, --patch-radius 2
                        2x2x2
          Patch radius for similarity measures. Default = 2x2x2

     -m, --patch-metric (PC)/MSQ
          Metric to be used in determining the most similar neighborhood patch. Options
          include Pearson's correlation (PC) and mean squares (MSQ). Default = PC (Pearson
          correlation).

     -s, --search-radius 3
                         3x3x3
                         searchRadiusMap.nii.gz
          Search radius for similarity measures. Default = 3x3x3. One can also specify an
          image where the value at the voxel specifies the isotropic search radius at that
          voxel.

     -e, --exclusion-image label[exclusionImage]
          Specify an exclusion region for the given label.

     -x, --mask-image maskImageFilename
          If a mask image is specified, fusion is only performed in the mask region.

     -o, --output labelFusionImage
                  intensityFusionImageFileNameFormat
                  [labelFusionImage,intensityFusionImageFileNameFormat,<labelPosteriorProbabilityImageFileNameFormat>,<atlasVotingWeightImageFileNameFormat>]
          The output is the intensity and/or label fusion image. Additional optional
          outputs include the label posterior probability images and the atlas voting
          weight images.

     --version
          Get version information.

     --help
          Print the help menu.
          <VALUES>: 1

```

@@

## Cortical thickness maps

@@

<!--
##  What about using both the T1 & T2?
-->

@@

-->

<!--
----

_So how does ATITH compare with ANTs, FS?_
-->
## Prediction from cortical thickness data

@@

-->

## Longitudinal processing

![](./longitudinal/figures/longitudinalPipeline.png)

@@

----

*  "_Hey, can I have the FreeSurfer measurements for the entorhinal cortex?_"
Sure, why not?---[Hasan, et al., J Neuroimaging](http://www.ncbi.nlm.nih.gov/pubmed/26565394)

# Current work and Advanced Normalization Tools in R (ANTsR)

## Multimodal Brain Tumor Segmentation (BRATS 2013)

![](./competitions/figures/brats2013results2.png)

[Tustison, et al., Optimal symmetric multimodal templates and concatenated random forests for
supervised brain tumor segmentation (simplified) with _ANTsR_, _Neuroinformatics_.](http://www.ncbi.nlm.nih.gov/pubmed/25433513)

## White matter hyperintensities in TBI

![](./wmhs/figures/wmhPipeline.png)

## Social behavior and immunity dysfunction in mice

![](./antsr/figures/filiano_rsfmri.png)

## Other ANTsR work

* [Pediatric template of brain perfusion](http://www.nature.com/articles/sdata20153)

* [Automated segmentation of chronic stroke lesions using LINDA: Lesion identification with neighborhood data analysis](http://www.ncbi.nlm.nih.gov/pubmed/26756101)

* [Eigenanatomy](http://www.ncbi.nlm.nih.gov/pubmed/25448483)

* Corrective learning for segmentation refinement

### 2016-07-17 mystyle.tex
ENH:  IBM presentation.

\pgfdeclareimage[height=0.1cm, width=1cm]{logo}{}
\logo{\pgfuseimage{logo}}
\institute{}
\definecolor{links}{HTML}{2A1B81}
\definecolor{mypink2}{RGB}{219, 48, 122}
\hypersetup{colorlinks,linkcolor=links,urlcolor=mypink2}
\usefonttheme{professionalfonts}
\setbeamerfont{note page}{family*=pplx,size=\footnotesize} % Palatino for notes
\usepackage{helvet}
\useinnertheme{rectangles}

>>>>

% \pgfdeclareimage[width=1cm]{logo}{./figures/monkeyTypewriter.png}
%\logo{\pgfuseimage{logo}}

\institute{University of Virginia}
\definecolor{links}{RGB}{42, 27, 129}
\definecolor{mypink2}{RGB}{219, 48, 122}
%\hypersetup{colorlinks,linkcolor=links,urlcolor=mypink2}
\usefonttheme{professionalfonts}

% \setbeamerfont{note page}{family*=pplx,size=\footnotesize} % Palatino for notes

\setbeamerfont{subtitle}{size=\small}

\definecolor{uvablue}{RGB}{0,85,150}
\definecolor{uvalibraryorange}{RGB}{252,175,23}
\definecolor{uvacream}{RGB}{241,229,199}
\definecolor{uvalightblue}{RGB}{163,220,230}

\setbeamercolor{block body}{bg=green,fg=green}
\setbeamercolor{block body alerted}{bg=green,fg=green}
\setbeamercolor{block body example}{bg=green,fg=green}

\setbeamercolor{caption name}{fg=uvablue}

\setbeamercolor{headline}{fg=uvacream,bg=uvacream}
\setbeamercolor{section}{fg=uvalibraryorange,bg=uvablue}
\setbeamercolor{frametitle}{fg=uvalibraryorange,bg=uvablue}
\setbeamercolor{palette primary}{bg=uvalibraryorange,fg=uvablue}
\setbeamercolor{palette secondary}{bg=uvablue,fg=uvablue}
\setbeamercolor{palette tertiary}{bg=uvalibraryorange,fg=uvablue}
\setbeamercolor{palette quarternary}{fg=uvalibraryorange,bg=uvablue}
\setbeamercolor{palette sidebar primary}{bg=uvalibraryorange,fg=uvablue}
\setbeamercolor{palette sidebar secondary}{fg=uvablue,bg=uvablue}
\setbeamercolor{palette sidebar tertiary}{fg=uvalibraryorange,bg=uvablue}
\setbeamercolor{palette sidebar quarternary}{fg=uvalibraryorange,bg=uvablue}
\setbeamercolor{structure}{bg=uvablue}

\useinnertheme{rectangles}

\titlegraphic{\vspace{-7.5mm}\includegraphics[width=0.45\paperwidth]{./figures/monkeyTypewriter.png}}
